A thesis draft

### 2018-09-28 draft.tex
Add technical analysis

As in~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the 
integration of multiple tools (some of them have been already briefly 
introduced in~\ref{chap:intro}). The tools were choosen after their 
analysis, where pro and cons have been studied and compared to the necessity of 
this thesis.

>>>>

As in~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the 
integration of multiple tools (some of them have been already briefly 
introduced in~\ref{chap:intro}). The tools were choosen after their 
analysis, where pro and cons have been studied and compared to the necessity of 
this thesis. Since the project has been developed with the cloud provided by 
the University of Padua, Openstack (which a product analysis can be found later 
in~\ref{chap:prjan:sec:openstack}) has been used as base for our deployments.

\section{Technical analysis}

As today, when a packets gets send from a seder $S$, to a receiver $R$, the 
packet gets travelling to te backbone receive appropriate in-hardware packet 
processing before being received by $R$. During this elaboration, it is 
important to maintain the transparency of the connection, so that the network 
users are not aware of the packets elaboration at all. To perform that, many 
solutions are available: TUN/TAP packet incapsulation, IP over IP or TCP 
session recreation\todo{Check if it's the same of Split TCP}.

TUN/TAP and IP over IP maintain the connection transparency incapsulating the 
packet in another one. In this way, the original packet remains preserved and it 
becomes the new packet payload\todo{Make an image showing a packet inside 
another packet, to make easy to understand what we're meaning here}, that can 
be elaborated and modified accordingly, until it gets decapsulated and sent to 
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet 
elaboration, since all the original headers were preserved (or slightly 
modified).

\todo{Explain TCP session recreation}

\section{Openstack}
\label{chap:prjan:sec:openstack}
Created in ??\todo{Find out Openstack date of creation}, 
Openstack allows on-permise cloud installation, using bare-metal resources to 
provide common cloud services as object storage, virtual machine deploy, 
virtual networking. Furthermore its modularity offers the possibility to add 
additional components, even proprietary, to achieve a complete cloud solution.
